% Pistes d'implémentation

\begin{frame}[c]
  \frametitle{ASP Implementation}

\tval{ASP}: Declarative programming

\quad Rule: \ex{$head \leftarrow \only<1>{body}\only<2->{A_1, ..., A_n, \neg A_{n+1}, ..., \neg A_m}.$}

\quad Fact: \ex{$head.$}

\quad Constraint: \ex{$\leftarrow body.$}

\quad Aggregate: \ex{$lower~\{~atoms~\}~upper \leftarrow body.$}

\pause[3]
\bigskip
Representation of PH / BRNs:

\quad Gene: \ex{$component(a, n).$}

\quad Action: \ex{$action(a, i, b, j, k).$}

\quad Cooperation: \ex{$cooperation(c, a, i, j).$}

\quad Useful rules: \ex{$component\_levels(X, 0..M) \leftarrow component(X, M).$}
\end{frame}



% Pistes d'implémentation

\begin{frame}[c]
  \frametitle{ASP Implementation}

\tval{ASP}: Declarative programming

\quad Rule: \texttt{\ex{head :- \only<1>{body}\only<2->{A$_1$, ..., A$_n$, $\neg$A$_{n+1}$, ..., $\neg$A$_m$}.}}

\quad Fact: \texttt{\ex{head.}}

\quad Constraint: \texttt{\ex{:- body.}}

\pause[3]
\bigskip
Example:

\texttt{\ex{%
~~~node(a). node(b). node(c).\\
~~~edge(a, b). edge(b, c). edge(a, c).\\
~~~edge(X,Y) :- edge(Y,X).
}}

\bigskip
Solving: find the biggest set of atoms satisfying the problem

\texttt{\console{%
~~~node(a) node(c) node(b)\\
~~~edge(a, b) edge(b, c) edge(a, c)\\
~~~edge(b, a) edge(c, b) edge(c, a)\\
}}

\end{frame}



\begin{frame}[c]
  \frametitle{ASP Implementation}

\tval{Cardinalities}: \quad
\texttt{\ex{%
\textit{min} \{ atom : enum \} \textit{max} :- body.
}}

\pause
\bigskip

\f Enumerate of all combinations:

\texttt{\ex{%
~~~color(red;green;blue).\\
~~~1 {attrib(X,C) : color(C)} 1 :- node(X).
}}

\texttt{\console{%
Answer~1:~attrib(b,red) attrib(c,red) attrib(a,red)\\
Answer~2:~attrib(b,red) attrib(c,red) attrib(a,blue)\\
Answer~3:~attrib(b,red) attrib(c,green) attrib(a,blue)\\
~~~$\vdots$\\
SATISFIABLE: 27 models
}}

\pause
\bigskip

\f Then reduce the number of answers with constraints:

\texttt{\ex{%
~~~:- attrib(X,C), attrib(Y,C), edge(X,Y).
}}

\texttt{\console{%
Answer~1:~attrib(b,green) attrib(c,blue) attrib(a,red)\\
Answer~2:~attrib(b,green) attrib(c,red) attrib(a,blue)\\
Answer~3:~attrib(b,blue) attrib(c,green) attrib(a,red)\\
~~~$\vdots$\\
SATISFIABLE: 6 models
}}

\end{frame}


\begin{frame}[c]
  \frametitle{Enumerating admissible Parametrizations}
  \framesubtitle{Implementation}

PH / GRN definitions:

\texttt{\ex{%
~~~component(a, 2).\\
~~~component(b, 1).\\
~~~action(b, 1, a, 1, 2).
}}

\bigskip
Useful rules:

\texttt{\ex{%
~~~component\_levels(X, 0..M) :- component(X, M).\\
~~~less\_active(X, P, Q) :-}} $K_{\texttt{X},\texttt{P}}$\text{ has less activators than }$K_{\texttt{X},\texttt{Q}}$\texttt{\ex{\\
~~~param\_inf(X, P, Q) :-}} $K_{\texttt{X},\texttt{P}} \preccurlyeq K_{\texttt{X},\texttt{Q}}$

\pause
\bigskip
Parameters enumeration with cardinalities:

\texttt{\ex{%
~~~1 \{ param(X, P, I) : component\_levels(X, I) \} :-\\
~~~~~param\_label(X, P).
}}

[\texttt{X}: component, \texttt{P}: parameter label, \texttt{I}: parameter value]

\pause
\bigskip
Parametrizations filtering with constraints:

\texttt{\ex{%
~~~:- less\_active(X, P, Q), not param\_inf(X, P, Q).
}}

[\texttt{X}: component, \texttt{P}, \texttt{Q}: parameter labels]

\end{frame}
